Linear Algebra as a Unifying Theory\\of Wireless Workload Modeling

### 2008-02-04 paper.tex
Added a TODO; other minor edits.

@@

Given an instance of the general matrix model, how do we produce an actual workload form it? Each row of the model is used to randomly generate the behavior of a single flow. The source and destination nodes of the flow are randomly chosen, using histogram vectors $\vec{s}$ and $\vec{d}$ as the proportional probabilities of each node being chosen.\footnote{Since a flow must have distinct source and destination nodes, this sampling must be done jointly, avoiding the collisions. The simplest technique is the rejection method: if the same node is chosen for both source and destination, reject that pair and begin the selection process again.}
For start and end times, a bin for each is chosen with probability proportional to the vector values; given a bin, a random value is uniformly chosen from the range of values in the bin.\footnote{The start time must precede the end time, so these choices must also be made jointly, enforcing this restriction. The rejection method is used.}
The first packet is sent at chosen start time; the size of each packet is sampled from the histogram of packet sizes, $\vec{z}$; the interval until the next packet is determined from the interval vector, $\vec{v}$. Specifically, an interval index, $k$, is chosen with probability proportional to $\vec{v}_k$; a second value, $u$, is chosen uniformly from $(0,1]$; the pair $\seq{k,u}$ is transformed back into a continuous time value using the ``dequantization'' function:
\begin{align}
\label{eqn:interval-dequantization}
\Di(k,u)=v_{\min}+(v_{\max}-v_{\min})\left(\frac{k-u}{d_v}\right)^{\frac{1}{\gamma}}.
\end{align}
The packet stream ends when a packet would be sent after the chosen end time of the flow.

>>>>

% TODO: talk about other vector-space representation: perfect representation, markov models, ... others?

@@

Given an instance of the general matrix model, how do we produce an actual workload form it? Each row of the model is used to randomly generate the behavior of a single flow. The source and destination nodes of the flow are randomly chosen, using histogram vectors $\vec{s}$ and $\vec{d}$ as the proportional probabilities of each node being chosen.\footnote{Since a flow must have distinct source and destination nodes, this sampling must be done jointly, avoiding the collisions. The simplest technique is the rejection method: if the same node is chosen for both source and destination, reject that pair and begin the selection process again.}
For start and end times, a bin for each is chosen with probability proportional to the vector values; given a bin, a random value is uniformly chosen from the range of values in the bin.\footnote{The start time must precede the end time, so these choices must also be made jointly, enforcing this restriction. The rejection method is used.}
The first packet is sent at chosen start time; the size of each packet is sampled from the histogram of packet sizes, $\vec{z}$; the interval until the next packet is determined from the interval vector, $\vec{v}$. Specifically, an interval index, $k$, is chosen with probability proportional to $\vec{v}(k)$; a second value, $u$, is chosen uniformly from $(0,1]$; the pair $\seq{k,u}$ is transformed back into a continuous time value using the ``dequantization'' function:
\begin{align}
\label{eqn:interval-dequantization}
\Di(k,u)=v_{\min}+(v_{\max}-v_{\min})\left(\frac{k-u}{d_v}\right)^{\frac{1}{\gamma}}.
\end{align}
The packet stream ends when a packet would be sent after the chosen end time of the flow.
